---
title: "test"
author: "maurizio"
date: "29/07/2019"
output: 
---


```{r, echo = FALSE, warning = FALSE, cache = FALSE, out.width = "70%", results = 'asis', message = FALSE, comment=FALSE, include=FALSE}

library(readxl)
library(dplyr)
library(lubridate)
library(tidyr)
library(readr)
library(stringr)
library(tools)
library(ggplot2)
library(ggpmisc)
library(xtable)
library(pander)
library(formattable)
library(rmarkdown)
library(knitr)
library(kableExtra)
library(forcats)
library(bookdown)
library(ggrepel)
library(httr)
library(scales)
library(RODBC)
library(mosaic)
library(mosaicData)
library(shiny)
library(odbc)
library(DBI)
library(flextable)
library(officer)
library(gridExtra)
library(RGraphics) 
library(requireR)
library(captioner)
library(citr)
library(cowplot)



```


EN NUMBER



``````{r, fig.height=5, fig.width=10, echo = FALSE, warning = FALSE, cache = FALSE, out.width = "70%", results = 'asis', message = FALSE, comment=FALSE}

## Create a connection with the Data Base
InterDB.path <- file.path("E:\\BKUP\\Desktop\\LCE_Template.GAS-PHASE.accdb")
InterDB <- RODBC::odbcConnectAccess2007(InterDB.path)
 ## Import the table/query

# Loading query
ISO13528_7_6_z.df <- sqlFetch(InterDB, "ISO 13528 (7_6)_z")[,c("code", "parameter", "z","run", "run (1-j-q)", "z_2+", "z_2-", "z_3+", "z_3-")]

# disconnect
close(InterDB)


for (i in unique(ISO13528_7_6_z.df$parameter)) {
    # Caption
  fig.nb <- grep(i, unique(ISO13528_7_6_z.df$parameter))
  Caption <-  paste0("Figure ", fig.nb,": Z’-score evaluations of CO measurements 
Scores are given for each participant and each tested concentration level (run). The assessment criteria are presented as z’=±2 (blue line) and z’=±3 (red line). They represent the limits for the questionable and unsatisfactory results")
  pander::pander(Caption)
  
  # gas selection
#ISO13528_7_6_z.df <- ISO13528_7_6_z.df %>%
  
# filter(code == "A")
  
  Tick.X <- unique(ISO13528_7_6_z.df[ISO13528_7_6_z.df$parameter == i, "run (1-j-q)"])
  fig <- ggplot(ISO13528_7_6_z.df %>% 
                  filter(parameter == i), 
                aes(x = `run (1-j-q)`, y = z, fill = code)) +
    theme_bw(base_size = 10) +
    geom_col(colour= "black", stat = "identity") +
    facet_grid(. ~ code) +
    
    ## axis.text for both axes
    
   labs(title = paste0("Parameter ", i), x = "", y = "z'-score") +
    scale_y_continuous(limit = c(-3.5, +3.5)) +
    scale_x_continuous(breaks = Tick.X) +
    geom_hline(yintercept = 2,  col = "blue", lty = 1) +
    geom_hline(yintercept = 3,  col = "red" , lty = 1) +
    geom_hline(yintercept = -2,  col = "blue", lty = 1) +
    geom_hline(yintercept = -3,  col = "red" , lty = 1) +
    # ggtitle(expression(paste("title position)"))) + 
    theme(plot.title = element_text(lineheight=.8, face="bold", size = 15, hjust = 0.5))
  print(fig)
  
}


```





Z-SCORE


```{r, echo = FALSE, warning = FALSE, cache = FALSE, out.width = "70%", results = 'asis', message = FALSE, comment=FALSE, include=FALSE}


## Create a connection with the Data Base
InterDB.path <- file.path("E:\\BKUP\\Desktop\\LCE_Template.GAS-PHASE.accdb")
InterDB <- RODBC::odbcConnectAccess2007(InterDB.path)
 ## Import the table/query

# Loading query
ISO13528_7_6_z.df <- sqlFetch(InterDB, "ISO 13528 (7_6)_z")[,c("code", "parameter", "z","run", "run (1-j-q)", "z_2+", "z_2-", "z_3+", "z_3-")]

# disconnect
close(InterDB)


for (i in unique(ISO13528_7_6_z.df$code)) {
    # Caption
  fig.nb <- grep(i, unique(ISO13528_7_6_z.df$code))
  Caption <-  paste0("Figure ", fig.nb,": Z’-score evaluations of CO measurements 
Scores are given for each participant and each tested concentration level (run). The assessment criteria are presented as z’=±2 (blue line) and z’=±3 (red line). They represent the limits for the questionable and unsatisfactory results")
  pander::pander(Caption)
  
  # gas selection
#ISO13528_7_6_z.df <- ISO13528_7_6_z.df %>%
  
# filter(code == "A")
  
  Tick.X <- ISO13528_7_6_z.df[ISO13528_7_6_z.df$code == i,"run (1-j-q)"]
  fig <- ggplot(ISO13528_7_6_z.df %>% 
                  filter(code == i), 
                aes(x = run, y = z, fill = parameter)) +
    theme_bw(base_size = 20) +
    geom_bar(colour= "black", stat = "identity") +
 
    ## axis.text for both axes
    
   labs(title = paste0("Lab ", i), x = "", y = "z'-score") +
    scale_y_continuous(limit = c(-3.5, +3.5)) +
    scale_x_discrete(labels = Tick.X) +
    geom_hline(yintercept = 2,  col = "blue", lty = 1) +
    geom_hline(yintercept = 3,  col = "red" , lty = 1) +
    geom_hline(yintercept = -2,  col = "blue", lty = 1) +
    geom_hline(yintercept = -3,  col = "red" , lty = 1) +
    # ggtitle(expression(paste("title position)"))) + 
    theme(plot.title = element_text(lineheight=.8, face="bold", size = 15, hjust = 0.5))
  print(fig)
  
}

```



```{r}
library(officer)
def_cell <- fp_cell(border = fp_border(color="#00FFFF"))
def_par <- fp_par(text.align = "center")
ft <- flextable(mtcars)
ft <- style( ft, pr_c = def_cell, pr_p = def_par, part = "all")
ft <- style(ft, ~ drat > 3.5, ~ vs + am + gear + carb,
pr_t = fp_text(color="red", italic = TRUE) )

ft <- flextable(mtcars)
ft <- bg(ft, bg = "#DDDDDD", part = "header")
ft

```
